% Previously titled Risk managemetn
% Now titled Project management, but basically just talk about risks



% Did any risks occur?
% How did you mitigate them?
% Talk about not having access to barefoot P4 stuff
% and delays
% mental health?
% thompson: "the plans and guidelines set out for the project were invaluable"
%   talk about how useful it was having made those plans


% Coles
  % talks just about agile, has no subsections

% Dutton
%   Subsections
%     Approach to Design and Development
%       Agile is gr9
%     Project Timeline
%       Why did the timeline chang,e and how did agile help
%     Tools and Techniques
%       The tools helped, and contributed to the success of the project
%   Also has an intro where she says these are fully discusses in section X but this evaluastes them


% Thompson
%   Subsections
%     Design Approach
%       no
%     Software Development Methodology
%       how did agile help
%     Project Schedule
%       why did the delays happen, + dutton
%     Tools
%       Which tools were best? + dutton
%
%     Management Approach
%       no
%     Risk Management
%     "Without these redundancies in place the project would not be at the stage it is now"
%     Talk about specific fuck ups, such as P4 issues

% Wyatt
%   No subsections
%   agile is gr9
%   tools
%   talking to supervisor helps


% -----------


%   Also has an intro where she says these are fully discusses in section X but this evaluastes them

\subsection{Software Development Methodology}
%       Agile is gr9
%       how did agile help
%   talking to supervisor helps
As discussed in section \ref{software_development_methodology}, this project used an agile methodology in order to adapt to changes which occured during the project. The flexibility provided by this methodology proved invaluable, due to the changes made to the project aims over the course of the project.
The methodology also encouraged the weekly meetings between the developer and the supervisor, which were crucial in keeping the project viable.



\subsection{Project Schedule}
%       why did the delays happen, + dutton
%       Why did the timeline chang,e and how did agile help
The final project timetable is shown in figure \ref{final_gantt_chart}. This changed from the initial project timetable shown in figure \ref{initial_gantt_chart} due to changes in the focus of the project, and due to issues occurring which made the initial timetable no longer viable.

An example of these issues is that resources to assist with development of a \textit{P4} based system which were due to be delivered by an external supplier early in term 2 were repeatedly delayed by the supplier, and ultimately were never delivered.
Since \textit{P4} is a relatively new language, the documentation and tutorials supplied with it still have much room for improvement. This imposed a short delay on the project timetable, as it was expected that the resources would be delivered.

Fortunately, the project was able to use its agile methodology to adapt to this and similar delays, and the final timetable was sufficient to complete the project aims.

\subsection{Tools}
A variety of different tools contributed to the success of the project, both in terms of streamlining development, and enhancing the project itself. In particular, \textit{Mininet} was a significant component of the implemented system, and once the developer gained familiarity with this component, offered many additional benefits which improved the functionality of the system. \textit{Git} was also a crucial management tool, allowing peace of mind during development that all code was saved and accessible, and allowing multiple components to be worked on simultaneously using \textit{Git}'s `branches'.

%       Which tools were best? + dutton
%       The tools helped, and contributed to the success of the project

\subsection{Risk Management}
% thompson: "the plans and guidelines set out for the project were invaluable"
%   talk about how useful it was having made those plans
%     "Without these redundancies in place the project would not be at the stage it is now"
%     Talk about specific fuck ups, such as P4 issues


% Did any risks occur?
% How did you mitigate them?
% Talk about not having access to barefoot P4 stuff
% and delays
% mental health?

The strategies defined in section \ref{risk_management} proved worthwhile over the course of the project, as some of them needed to be actioned. While the primary development machine did not fail entirely, errors did occasionally occur which caused recently written files to be lost. Fortunately, since files were uploaded to \textit{GitHub} regularly, the majority of these files were able to be restored. This saved a significant amount of time and effort during the project.
