% "As a member of the BCS"
% Follow BCS code of conduct / code of practice?
% say something about how I aim to follow BCS code of conduct anyway
% Follow industry standars
%
% user's sense of security maintaines so user feels they can trust the app
%
% describe in what ways you're following BCS

Since the developer is a member of the BCS, following the BCS Code of Conduct \cite{bcs_code_of_conduct} is general professional aim, not limited to the scope of this project. The BCS Code of Conduct comprises four key principles:
\begin{enumerate}
  \item You make IT for everyone
  \item Show what you know, learn what you don't
  \item Respect the organisation or individual you work for
  \item Keep IT real. Keep IT professional. Pass IT on.
\end{enumerate}

These principles have been consciously followed throughout this project. By making the implemented aspect of the project open-source, the first principle is being followed. The IT application created as a result of this project is being made available for everyone. This project has involved a great deal of learning for the developer in order to gain the necessary skills to research and develop the project. In addition, the background knowledge discussed in section \ref{background_knowledge} was used as a basis for the project. This demonstrates the second key principle. The third key principle has been taken into account whenever in contact with members of the University of Warwick. Finally, this project represents a key area of interest for the developer and as such has been motivated to develop and share the knowledge acquired over the course of the project, exemplifying the fourth key principle.
