% Get these from specification and progress report
% Add some commentary about how they are outdated because
  % they reflect the system you were building at the start of the project
  % You're agile, so it changed
  % the new system is better and more feasible
  % reference the new ones
  % reference the spec
% have subsections for func and non func

Due to the agile nature of the project, the requirements for this project have undergone a number of revisions over the course of the project.
The initial requirements were written as part of the project specification (shown in appendix \ref{initial_spec}) at the start of the project, and these reflect the intentions for the project at that time.
The revisions made to the project since these requirements were written has rendered many of these redundant, and these are shown to illustrate some of the changes the project has undergone.

\subsection{Initial Functional Requirements}
\label{initial_functional_requirements}

\begin{enumerate}[label=\textbf{F\arabic*:}]
  \item The system \textbf{must} be able to analyse packets at layer 2 of the OSI network model.
  \item The system \textbf{must} be able to send packets to the correct port based on MAC addresses.
  \item The system \textbf{must} be able to store MAC address tables.
  \item The system \textbf{must} be able to dynamically update MAC address tables.
  \item The average latency of the system \textbf{must} be measured.
  \item The throughput of the system \textbf{must} be measured.
  \item The system \textbf{should} be able to analyse packets at layer 3 of the OSI network model.
  \item The system \textbf{could} be able to analyse packets at layer 7 of the OSI network model.
  \item The system \textbf{could} be able to detect basic network attacks (such as TCP SYN Flooding \cite{rfc4987}).
  \item The system \textbf{could} implement features of a basic firewall (such as packet filtering \cite{rfc2979}).
\end{enumerate}

\subsection{Initial Non-Functional Requirements}
\label{initial_non_functional_requirements}

\begin{enumerate}[label=\textbf{NF\arabic*:}]
  \item The system \textbf{should} be scalable.
  \item The system \textbf{should} be efficient.
  \item All code for the system \textbf{should} be well-documented and maintainable.
\end{enumerate}
